---
title: "1.4 Greta"
author: "Greta Lotz"
date: "2023-12-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      error = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      comment = NA)
```

```{r packages, include = T}
library(tidyverse)
library(rvest)
library(httr)
library(knitr)
library(xml2) 
library(stringr)
library(purrr)
library(haven)
library(scales)
library(gt)
library(gtExtras)

```

1.4 Perceived hatefulness of social media post
Create a gt/gtExtras table that reports the aggregated perceived hatefulness of a set of social media posts, following good practice of visualization. For this task, consider the following:
• Some guidance for the data preparation:
o The content of the social media posts is stored in two types of variables:
vig_{x}_topic and vig_{x}_sender_message. Every respondent evaluated 8 different messages, which is why x goes from 1 to 8. The perception of hatefulness is stored in the variables vig_{x}_hateful.
o Drop observations where vig_1_hateful is missing.
o Recodethevig_{x}_topic variables according to the following scheme:
gender = "Women", ideologydems = "Democrats", ideologyreps =
"Republicans", muslim = "Muslim immigrants".
o Construct the full content of the message by pasting together the strings
of the recoded vig_{x}_topic and vig_{x}_sender_message variables. For instance, one of the full messages reads: “Republicans should be stopped from spreading falsehoods.”
o For the evaluation, you should average across all evaluated vignettes across all responses, i.e. your unit of analysis is vignettes, not respondents.
• Your table should contain the following information: (1) The message text, (2) the mean and standard deviation of the hatefulness rating by message, and (3) a
barplot displaying the distribution of hatefulness ratings 1 to 5 per message.
• The average hatefulness column should be colored by value.
• The table should provide a meaningful title and description, making it a
standalone product that speaks for itself.
```{r load and remove NA}
df_survey <- readRDS("survey/meof_usa_survey_df.rds")

# Drop observations where vig_1_hateful is missing
df_survey <- df_survey[!is.na(df_survey$vig_1_hateful), ]

```

```{r recode vignette topic}

# Recoding the vig_(x)_topic variable

#print(df_survey$vig_1_topic)

# Vector with recoding rules for loop
recoding_rules <- c("gender" = "Women",
                    "ideologydems" = "Democrats",
                    "ideologyreps" = "Republicans",
                    "muslim" = "Muslim immigrants")

# Loop through the variables and apply the recoding rules
for (var_suffix in 1:8) {
  var_name <- paste0("vig_", var_suffix, "_topic")
  df_survey <- df_survey %>%
    mutate_at(vars(starts_with(var_name)), funs(recode(., !!!recoding_rules)))
}

#print(df_survey$vig_1_topic)
```

```{r combine variables topic and sender_message}
# Combine variables _topic and _sender_message 1-8 into 8 new variables with the full string

#print(df_survey$vig_1_sender_message)
# First, clean up the string "Women should be caring mothers and not pursue \r\na selfish career." 

# Loop through the variables and process the sender messages
for (var_suffix in 1:8) {
  sender_message_var <- paste0("vig_", var_suffix, "_sender_message")
  df_survey[[sender_message_var]] <- gsub("[\r\n\t]", " ", df_survey[[sender_message_var]])
  df_survey[[sender_message_var]] <- gsub("\\s+", " ", df_survey[[sender_message_var]])
}

#print(df_survey$vig_8_sender_message)


# Construct full message for vig_1

# Test for one
# df_survey <- df_survey %>%
# mutate(full_message_vig_1 = paste(vig_1_topic, vig_1_sender_message, sep = " "))
#print(df_survey$full_message_vig_1)

# Loop through the variables and create new columns
for (var_suffix in 1:8) {
  topic_var <- paste0("vig_", var_suffix, "_topic")
  message_var <- paste0("vig_", var_suffix, "_sender_message")
  new_column_name <- paste0("full_message_vig_", var_suffix)
  
  df_survey <- df_survey %>%
    mutate(!!new_column_name := paste(.data[[topic_var]], .data[[message_var]], sep = " "))
}

# Display the new columns to verify
#new_column_names <- grep("^full_message_vig_", names(df_survey), value = TRUE)
#print(df_survey[, new_column_names, drop = FALSE])
```


```{r create the table 1}
# Create a subset with the relevant variables (optional, for my own improved workflow)

# Extract the columns for each x in the range 1 to 8
selected_columns <- c("personid", 
                      paste0("vig_", 1:8, "_hateful"), 
                      paste0("full_message_vig_", 1:8))
df_subset <- df_survey[selected_columns]

#print(df_subset)


```

```{r}
# Create a data frame with unique message texts
unique_messages <- data.frame(message = unique(unlist(df_subset[, grep("^full_message_vig_", names(df_subset))])))
# There are 37 unique statements that were evaluated
```

```{r transform into long format}

# Specify the column names for pivoting
cols_to_long <- c(paste0("full_message_vig_", 1:8), paste0("vig_", 1:8, "_hateful"))

# Use pivot_longer to transform the data frame to long format
df_subset_long <- pivot_longer(df_subset, cols = cols_to_long, 
                        names_to = c(".value", "vig_num"), 
                        names_pattern = "(\\w+)_([0-9]+)")

# Rename the columns as needed
colnames(df_subset_long) <- c("personid", "vig_num", "full_message", "rating_hateful")

# Convert vig_num to numeric if needed
df_subset_long$vig_num <- as.numeric(df_subset_long$vig_num)

# View the resulting data frame
print(df_subset_long)
```

```{r}

# Test to find out if method works
# Define the specific message
target_message <- "Women should not be allowed to serve in the army."

# Create a subset with selected variables for the target message FOR VIG_1 ONLY
subset_women_army <- df_subset_long %>%
  filter(select(., starts_with("full_message")) == target_message) %>%
  select(personid, full_message, rating_hateful)

# Print the subset
print(subset_women_army)

# Calculate mean and standard deviation for the hateful ratings in the subset
subset_women_army <- subset_women_army %>%
  mutate(
    mean_hatefulness = mean(rating_hateful, na.rm = TRUE),
    sd_hatefulness = sd(rating_hateful, na.rm = TRUE)
  )

# Print the updated subset
print(subset_women_army)
```

```{r}



```

```{r}

# Create a data frame to store the results
message_stats <- data.frame(message = unique_messages$message)

# Calculate mean and standard deviation for each message
for (var_suffix in 1:8) {
  #topic_var <- paste0("vig_", var_suffix, "_topic")
  message_var <- paste0("full_message_vig_", var_suffix)
  rating_var <- paste0("vig_", var_suffix, "_hateful")
  
  # Create a new column for each vig_x_hateful variable
  message_stats <- message_stats %>%
    left_join(
      df_subset %>% 
        select(message = !!message_var, rating = !!rating_var) %>% 
        group_by(message) %>% 
        summarise(
          mean_hatefulness = mean(rating, na.rm = TRUE),
          sd_hatefulness = sd(rating, na.rm = TRUE)
        ),
      by = "message"
    )
}

# Print the results
print(message_stats)


```


```{r plot, echo=FALSE}

```


